Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2025-07-04 Latex_files/Thesis/main_win.tex
updates to chapter 4, among others
27/06/2025 chapters 1,3,4 and structural changes
fleshing out QPD chapter and edits to new chp 3&6

\documentclass[a4paper,oneside,11pt]{book}
\setcounter{secnumdepth}{3}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
%\usepackage{cite}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[strict]{changepage}
\usepackage{graphicx}
\graphicspath{{C:/Users/xbb16146/dmaciver97/Latex_files/Thesis/figs}}
\usepackage{sidecap}
% Page Margins - Strath Requirement
\usepackage[left=4cm,right=2.5cm,top=2cm,bottom=4cm,includehead,includefoot,headheight=15pt]{geometry}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{Appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of fluid shear rates via galvano mirror}
An alternative approach to generating fluid shear is to use a 
galvano-mirror to rapidly move a trapped particle in a bulk 
fluid. While typically galvano and gimble mirrors are used to 
trap multiple particles simultaneously, a single micro sphere 
can be moved quickly through a fluid along a preset path. The 
only limitation on the particle's speed being the ratio of the 
trap stiffness to the drag force. For low Reynolds numbers we 
can assume that the fluid flow is inversely proportional to the
distance from the particle surface (see Eq.~\eqref{eq:birefringent_shear})

@@

\section{Approximation of Area growth rate}
Data collected from \cite{Li1992} provides face growth rates 
for glycine seed crystals in supersaturated solutions. The 
reported growth rates are given in terms of $\mu m/sec$, in 
order to compare to the laser induced nucleation events we 
need some method of converting to area units. In \cite{Li1992}
the seed crystals are viewed from a top down perspective with
the edges marked $L_b$ and $L_c$. The authors calculated the 
face growth rates by:
\begin{align}
	G_{011} = \frac{1}{2}sin(67.5^\circ)\frac{dL_c}{dt} \\
	G_{010} = \frac{1}{2}sin(68.5^\circ)\frac{dL_b}{dt}
\end{align}

>>>>

\documentclass[a4paper,oneside,11pt]{book}
\setcounter{secnumdepth}{3}
\usepackage{amsbsy}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{mathrsfs}
\usepackage{color}
\usepackage[hidelinks]{hyperref}
\usepackage{textalpha}
\usepackage{enumitem}
\usepackage{epsfig}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[strict]{changepage}
\usepackage{graphicx}
\graphicspath{{C:/Users/xbb16146/dmaciver97/Latex_files/Thesis/figs}}
\usepackage{sidecap}
% Page Margins - Strath Requirement
\usepackage[left=4cm,right=2.5cm,top=2cm,bottom=4cm,includehead,includefoot,headheight=15pt]{geometry}

@@

\input{chapters/chapter 6/main}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\chapter{Appendix}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Estimation of fluid shear rates via galvano mirror}
\label{sec.shear_rate_calcs}
An alternative approach to generating fluid shear is to use a 
galvano-mirror to rapidly move a trapped particle in a bulk 
fluid. While typically galvano and gimble mirrors are used to 
trap multiple particles simultaneously, a single micro sphere 
can be moved quickly through a fluid along a preset path. The 
only limitation on the particle's speed being the ratio of the 
trap stiffness to the drag force. For low Reynolds numbers we 
can assume that the fluid flow is inversely proportional to the
distance from the particle surface (see Eq.~\eqref{eq:birefringent_shear})

@@

\section{Approximation of Area growth rate}
\label{sec.growth_rate_calcs}
Data collected from \cite{Li1992} provides face growth rates 
for glycine seed crystals in supersaturated solutions. The 
reported growth rates are given in terms of $\mu m/sec$, in 
order to compare to the laser induced nucleation events we 
need some method of converting to area units. In \cite{Li1992}
the seed crystals are viewed from a top down perspective with
the edges marked $L_b$ and $L_c$. The authors calculated the 
face growth rates by:
\begin{align}
	G_{011} = \frac{1}{2}sin(67.5^\circ)\frac{dL_c}{dt} \\
	G_{010} = \frac{1}{2}sin(68.5^\circ)\frac{dL_b}{dt}
\end{align}
